Draft Documents

### 2022-11-16 src/draft.Rmd
I'm fucking done

```{r cars}
summary(lm(formula = pov ~ income,data = train)) #0.6201
```

Since income as a predictor brought the highest adjusted r-value, we add another predictor to income to find the predictor added to income which produced the highest adjusted r-value. reg as a predictor has the highest adjusted r-value=0.7181

@@

The forward selection process continues and lgdp.pc is the new predictor added that produced highest adjusted r-square=0.7492
```{r}
summary(lm(formula = pov ~ lgdp.pc+income+reg,data = train)) #0.7492
```

The addition of predictor gdp.pc produces the highest adjusted r-square value above 0.75, adjusted r-square=0.7703
```{r}
summary(lm(formula = pov ~ gdp.pc+income+reg+lgdp.pc,data = train)) #0.7703
```

@@

  data.frame(
    MSE = mse,
    MAE = mae,
    RMSE = rmse,
    MAPE = mape
  )
}
predicted<-predict(lm1,newdata=test)
actual<-test$pov
df23<-na.omit(data.frame(actual,predicted))
ac<-df23$actual
pr<-df23$predicted
eval.metrics.linreg(ac,pr)
```

###  3.3.3. Interpretation
gdp per capital, income class and region of the country can provide a model to predict the poverty headcount ratio in a country.

@@

```{r}
set.seed(1984)
# split data
seeds <- countries1 %>% 
  group_by(country.code) %>% 
  filter(row_number() == 1)

@@

res <- do.call(rbind, lapply(models, \(f) coefficients(f$model)[var,]))
kable(res)
```

@@

@@

>>>>

```{r cars}
summary(lm(formula = pov ~ income,data = train)) #0.6201
```
Since income as a predictor brought the highest adjusted r-value, we add another predictor to income to find the predictor added to income which produced the highest adjusted r-value. reg as a predictor has the highest adjusted r-value=0.7181

@@

The forward selection process continues and lgdp.pc is the new predictor added that produced highest adjusted r-square=0.7492
```{r}
summary(lm(formula = pov ~ lgdp.pc+income+reg,data = train)) #0.7492
```
The addition of predictor gdp.pc produces the highest adjusted r-square value above 0.75, adjusted r-square=0.7703
```{r}
summary(lm(formula = pov ~ gdp.pc+income+reg+lgdp.pc,data = train)) #0.7703
```

@@

  data.frame(
    MSE = mse,
    MAE = mae,
    RMSE = rmse,
    MAPE = mape
  )
}
predicted<-predict(lm1,newdata=test)
actual<-test$pov
df23<-na.omit(data.frame(actual,predicted))
ac<-df23$actual
pr<-df23$predicted
eval.metrics.linreg(ac,pr)
```
###  3.3.3. Interpretation
gdp per capital, income class and region of the country can provide a model to predict the poverty headcount ratio in a country.

@@

```{r}
set.seed(1984)
# split data, make sure all the coutries
seeds <- countries1 %>% 
  group_by(country.code) %>% 
  filter(row_number() == 1)

@@

res <- do.call(rbind, lapply(models, \(f) coefficients(f$model)[var,]))
res <- cbind(data.frame(Set = 1:3), res)
kable(res)
```

@@

These data seems valid and there is no convincing reasons to remove them from the model (in the case of Guinea and Gambia, maybe there was some false reports because the jump were quite suspicious, but we need more evidence to conclude that they are false data).

@@

Final model coefficients (exclude `country.code`):

res <- do.call(rbind, lapply(models, \(f) coefficients(f$model)[var,]))
res <- cbind(data.frame(Set = 1:3), res)
kable(res)
```

We should convert them to un-standardised value for easier interepretation.

res <- do.call(rbind, lapply(models, \(f) {
  # get scaler saved in the model
  scaler <- f$scaler
  # categorical has scaler = 1
  scaler[c("incomeL","incomeLM","incomeUM")] <- 1
  # beta = std.beta * sigma_y / sigma_x
  coefficients(f$model)[var,] * scaler['pov'] / scaler[var]
}))
kable(res)
```
